TRITON: Globally Consistent Sim-to-Real Transfer

### 2022-06-02 CORL/example.tex
Changed title to "TRITON: Globally Consistent Sim-to-Real Transfer"
Imports stuff
Added incomplete introduction

% \usepackage{corl_2022} % Use this for the initial submission.
\usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
%\usepackage[preprint]{corl_2022} % Uncomment for pre-prints (e.g., arxiv); This is like ``final'', but will remove the CORL footnote.

\title{Formatting Instructions for CoRL 2022}

@@

    Submission to CoRL 2022 will be entirely electronic, via a web site (not email). Information about the submission process and \LaTeX{} templates are available on the conference web site at \url{http://www.robot-learning.org/}. For camera ready submission, use the \texttt{final} option for the \texttt{\textbackslash usepackage} command.

>>>>

% \usepackage{corl_2022} % Use this for the initial submission.
\usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
\usepackage{graphicx}
\graphicspath{ {../images} }

%\usepackage[preprint]{corl_2022} % Uncomment for pre-prints (e.g., arxiv); This is like ``final'', but will remove the CORL footnote.

\title{TRITON: Globally Consistent Sim-to-Real Transfer}

@@

	Recently, several sim to real algorithms have come out that are based on image to image translation. [Citations]
	These are used for training robots using pixel-based reinforcement learning.
	They demonstrated that better image translation algorithms yielded notable improvements in robotic benchmarks.
	At the same time, there is a lot of research on differentiable rendering,
		a topic which produced papers such as NERF which attempt to capture 3d representations of the real world.
	However, most of these approaches are either supervised or involve only camera movements [citations].
	One paper that came out recently combined both image translation and differentiable rendering in an unsupervised manner to create view-consistent models of human organs [citation].
	This paper too, though, was limited to only camera movements.

	The motivation for this paper is to create a temporally consistent sim-to-real image translation algorithm that will look the same from multiple camera angles simultaneuously, keeps all semantic details 
	[[I'll finish this later...lets work on the meat of the paper first...]]
